### 2023-04-10 main/chapter_theory.tex
begin cross-section

\subsection{Specific simplified models}
\TODO{add citations}
Two specific simplified supersymmetric models are studied in this thesis.
These models were selected for the \atlas\ $\twoljets$
search~\cite{atlas2022searches},
presented in Chapter~\ref{chapter:2ljets},
because they are well-studied but not-yet excluded models that can affect the
data in its targetted signature of data with two charged leptons,
hadronic jets, and missing transverse momentum.
Within the context of $\twoljets$, we name these two simplified models
`C1N2' and `GMSB'.

@@

\paragraph{GMSB.}
As described earlier in Section~\ref{sec:theory_susy}, GMSB models offer a
general mechanism to break supersymmetry by communicating some symmetry
breaking down from high mass scales~\cite{Meade:2008wd,SUSY-2018-02}.
The specific GMSB model used in the \atlas\ $\twoljets$ search
(and referred to as simply GMSB in its context) is a simplified model that
captures broad patterns of plausible behaviours in an experimentally pragmatic
format.
Under this GMSB model, visible signatures are generated by decays higgsino-like
neutralinos to Standard Model particles and a gravitino LSP, specifically
$\neutralino_1 \to Z/h + \gravitino$.
% TODO diverse decay channels
% TODO diverse initial states

\subsubsection{Cross-sections}
\TODO{Cross-sections}

>>>>

\subsection{Specific simplified models}
Two specific simplified supersymmetric models are studied in this thesis.
These models were selected for the \atlas\ $\twoljets$
search~\cite{atlas2022searches},
presented in Chapter~\ref{chapter:2ljets},
because they are well-studied but not-yet excluded models that can affect the
data in its targetted signature of data with two charged leptons,
hadronic jets, and missing transverse momentum.
Within the context of $\twoljets$, we name these two simplified models
`C1N2' and `GMSB'.

@@

\paragraph{GMSB.}
As described earlier in Section~\ref{sec:theory_susy}, GMSB models offer a
general mechanism to break supersymmetry by communicating some symmetry
breaking down from high mass scales~\cite{Meade:2008wd,SUSY-2018-02}.
The specific GMSB model used in the \atlas\ $\twoljets$ search
(and referred to as simply GMSB in its context) is a simplified model that
captures broad patterns of plausible behaviours in an experimentally pragmatic
format.
Under this GMSB model, visible signatures are generated by decays higgsino-like
neutralinos to Standard Model particles and a gravitino LSP, specifically
$\neutralino_1 \to Z/h + \gravitino$ from each side of a
$\neutralino_1 \neutralino_1$ pair production event.

We are experimentally interested in this decay mode because the $Z$ and Higgs
bosons can decay to diverse Standard Model decay products.
Again, the \atlas\ $\twoljets$ search chooses to target this model because
a significant decay mode includes $Z \to \ell^+\ell^-$, jets, and invisible
particles giving missing transverse momentum.
This simplified GMSB model also chooses to make the SUSY mass spectrum
`compressed', meaning that there are small mass differences between
$\neutralino_1$ and the slightly-heavier $\neutralino_2$ and $\chargino_2$.
This choice creates diverse initial states, since the hard scatter events can
emit various different pairs of heavier gaugino species and they will all decay
via unobservably soft emissions to produce the same
$\neutralino_1 \neutralino_1$ target
pair~\cite{atlas2022searches,hepdata.116034}.

\subsubsection{Cross-sections}
A substantial production cross-section is a necessary condition for a process
to be observable with finite data.
The Run~2 dataset studied by our $\twoljets$ search comprises
$L = 139\,\mathrm{fb}^{-1}$
of proton-proton collisions, meaning that a process with production
cross-section $\sigma = 1\,\mathrm{fb}$
should occur in the data with a Poisson mean of $\mu = L \sigma = 139$ times.
To achieve mean $\mu \geq 1$ event in the dataset, a process needs a cross-section
at least $1 / L \approx 7\,\mathrm{pb}$.

Cross-sections for the $\twoljets$ C1N2 and GMSB models are determined by two
factors: production cross-section and the decay branching fraction.
Each process pair-produces some heavy parent particles, so their production
cross-sections scale down with the parent particle mass
as both parton distribution hard-scatter matrix element
are pushed to harder scales.
For mass scale $q$, these three factors combine to an approximate scaling
of $\sigma \sim q^{-6}$ in the several-hundred-$\,\eV[G]$ regime.
Branching fractions in decay further reduce the observable cross-sections in
our selected decay channels; however, these are constant factors that do not
scale with parent mass.

\TODO{figure}

\TODO{example numbers}
